How is active school travel framed in Ontario, Canada?

### 2022-04-22 AST-Framing-Ontario/AST-Framing-Ontario.tex
Revised version of paper

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={The framing of active school travel in Ontario, Canada, as a health and built environment issue},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{The framing of active school travel in Ontario, Canada, as a
health and built environment issue}
    \author[Some Department]{Author 1\corref{1}}
   \ead{author1@example.com} 
    \author[Some Department]{Author 2}
   \ead{author2@example.com} 
    \author[Another University]{Author 3\corref{2}}
   \ead{author3@example.com} 
    \author[Some Institute]{Author 4\corref{2}}
   \ead{author4@example.com} 
    \author[Some University]{Author 5}
   \ead{author5@example.com} 
    \author[Some Department]{Author 6}
   \ead{author6@example.com} 
      \address[Some Department]{Department, Street, City, Province,
Postal Code}
    \address[Another University]{Department, Street, City, Province,
Postal Code}
    \address[Some Institute]{Street, City, Province, Postal Code}
    \address[Some University]{Department, Street, City, Province, Postal
Code}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

  \begin{abstract}
  This is the abstract.

  It consists of two paragraphs.
  \end{abstract}

@@

\textbf{\emph{Background}}:\\
\textbf{\emph{Methods}}:\\
\textbf{\emph{Results}}: \textbf{\emph{Conclusions}}:

@@

Rates of walking and bicycling to school, commonly known as active
school travel (AST), have been declining in Canada and the United States
for decades (Rothman et al., 2018). However, the appetite for AST may be
high in many Canadian communities. For instance, in a study conducted in
Toronto, Ontario, 40\% of children who are driven to school would like
to travel by bicycle instead (Larouche et al., 2016). The study also
reported that less than 3\% of respondents actually cycled, despite the
vast majority having access to a bicycle and living within a short and
bikeable distance to school. Another study based in London, Ontario,
reported similar findings with respect to children's preference for
active travel (Larsen et al., 2012). From a public health perspective,
increasing the use of active modes to school represents a major
opportunity to improve children's health and wellbeing.

The Government of Ontario, in Canada, has striven to promote this trend,
and created a fund in 2017 to support communities across the province to
develop AST initiatives. Green Communities Canada runs the program,
called \emph{Ontario Active School Travel} (Canada, 2020a). As of
December 2021, OAST has awarded over CAD 2 million and provided
resources to over 25 projects across Ontario. Many communities
implemented school travel planning (STP), along with encouraging
activities like walking school buses and developed resources for schools
and parents, among other actions (see Canada, 2020b). In this context,
STP is a popular ``school-specific'' intervention led by a facilitator
who brings together a committee of stakeholders from diverse sectors
including education, planning, transportation, and public health to
develop action plans (Buliung et al., 2011; Mammen et al., 2014a). The
five-step process involves identifying barriers to AST based on the
local context and implementing approaches or activities following the
4E's that make AST safer and more convenient: 1) setup of the program;
2) data collection and problem identification; 3) action planning; 4)
implementation; 5) monitoring and evaluation (Buliung et al., 2011; Lang
et al., 2011).

@@

More recently, the literature has explored the link between transport
and children's wellbeing (Waygood et al., 2020), with relevant
applications to the study of travel satisfaction (van den Berg et al.,
2020; Westman et al., 2017b). Being driven to school reduces community
interactions for children, which may negatively impact their social
wellbeing (Waygood and Friman, 2015). In contrast, walking and cycling
give children opportunities to socialize with friends or siblings
(Michail et al., 2021). This is something that children seem to value
(Zwerts et al., 2010) and that tracks with findings among university
students (Paez and Whalen, 2010). More generally, social connections
through travel appear to be important for wellbeing. Furthermore, AST
can provide opportunities for children to engage with natural
environments (Fusco et al., 2012; Romero, 2015).

@@

Factors that influence AST have been presented and organized using a
socio-ecological model (SEM) (Mitra, 2013) or systems model (Badland et
al., 2016) whereby children's travel behaviour is understood within the
context of household, social, neighbourhood, and policy environments.
The SEM comes from the field of public health and is a useful framework
for understanding complex health behaviours, such as walking and cycling
habits, This model helps to identify multiple determinants that need to
be addressed by interventions to facilitate behaviour change. The
consensus in the literature is that interventions should target multiple
levels in order to increase levels of healthy and physically active
modes of travel to school (Mitra, 2013). Rather than describing an
extensive list of factors that influence AST and mode choice in Canada
(e.g., Mammen et al., 2012; Mitra, 2013; Rothman et al., 2018; Wilson et
al., 2018), we discuss a few potentially modifiable determinants that
may be targeted for change through STP.

At the individual level, age is often positively associated with AST
(Mammen et al., 2012; Stark et al., 2018; Wilson et al., 2018). There is
evidence that gender is a determinant of AST, and that boys are more
likely to travel using active modes than girls, although this is not a
strong or consistent finding (Rothman et al., 2018; Schoeppe et al.,
2015). Children's mode choice to school is strongly influenced by their
parents' travel behaviours and the complexity of their household's
travel needs (Buliung et al., 2021), as well as the frequency of
parental support (\textbf{mahDoesParentalSupport2017a?}). This indicates
that shifting parental perceptions and habits is important. Convenience
and inclement weather have been cited by parents as barriers to AST
(Buliung et al., 2011). Parental perceptions of the built or school
environment (De Meester et al., 2014; Panter et al., 2010) and their
children's skills (Mammen et al., 2012;
\textbf{faulknerWhatQuickestEasiest2010?}) also influence mode choice to
school.

Distance between home and school is most strongly associated with AST
(Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009; Rothman et
al., 2018) with less AST reported among children who have to travel
farther to school - low density suburban development tends to increase
the need for movement, and the reliance on motorized modes (Farber and
Páez, 2011). Many studies have also found that the quality of the built
environment along the route to school and around the school site (Ikeda
et al., 2018; Rothman et al., 2021) and provision of active travel
infrastructure (Chen et al., 2018; Pont et al., 2009) facilitate AST.
Canadian youth report that they feel most safe bicycling on streets in
their neighbourhood or that have low volumes of traffic
(\textbf{TACbikeinfra2020?}). Finally, concerns about traffic and
strangers have been reported by parents who drive their children to
school (Mammen et al., 2012), which highlights that the volume and speed
of cars can be a concern or deterrent for AST.

@@

School travel planning (STP) has been implemented in Canada since at
least the late 2000s. Within the STP process, facilitators generally
establish multi-sector committees who intervene at the participating
school through a range of activities related to the 4E's consisting of
\emph{education} strategies, \emph{encouragement} through in-person
events or programs, \emph{engineering} improvements to or around the
school site, and \emph{enforcement} of traffic speeds around schools
(Lang et al., 2011; Mammen et al., 2014b). The first large-scale
evaluation of STP as an intervention in Canada took place at twelve
schools across the country, including four in Ontario, using parental
surveys to measure changes in travel behaviour and perceptions (Buliung
et al., 2011). Assessments of the efficacy of STP (Buttazzoni et al.,
2019; Mammen et al., 2014b) indicate that it has the potential to
encourage behaviour change and adoption of AST. STP facilitators have
recommended that additional time and resources are needed to improve the
efficacy of STP (Mammen et al., 2015), which highlights that long-term
and sustained efforts driven at the policy level are required to address
declining rates of AST.

How AST is framed seems particularly important to shift parental
attitudes and perceptions given their reported influence on children's
travel mode to school. STP activities heavily focus on education or
encouragement (Buliung et al., 2011; Buttazzoni et al., 2018; Mammen et
al., 2014b), but parents may not always be receptive to the goals of STP
and may be resistant to behaviour change (Buttazzoni et al., 2018).
Parents have been found to express different understandings, language,
and perceptions than planners of how the built environment can influence
school travel (Buliung et al., 2021). This is also true when it comes to
other factors like convenience of different modes to school (Lang et
al., 2011). STP stakeholders must pay special attention to parents'
understanding of the decline of AST as a problem, which may affect their
receptivity to proposed solutions.

The ``central organizing idea or story line'' of AST, to apply the
definition of framing from Gamson and Modigliani (1987), could also
affect broader support in the community. Municipal representatives are
perceived to be instrumental but the involvement of other stakeholder
groups (e.g., busing consortia representatives and local residents) can
be lacking (Buttazzoni et al., 2018). In Ontario, it is reasonable to
say that AST has become a policy issue on the education and public
health agendas, supported, albeit in a modest way, by financial
contributions from the provincial government\footnote{To put the CAD 2
  million invested by the province in the Ontario Active School Travel
  program, a city such as Hamilton budgeted in excess of CAD 91 million
  on road maintenance and construction in 2016 alone; see:
  https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets}.
Still, the support from a range of municipal representatives (see
Buttazzoni et al., 2018; Mammen et al., 2015) demonstrates that the AST
issue is on the political agenda. However, it is unknown to what degree
the general public (i.e., local residents) has been exposed to messaging
about AST.

@@

@@

We also manually removed any extraneous material in the academic papers
that did not pertain to AST specifically. This included footnotes,
references, acknowledgments, and conflict of interest statements in the
academic papers. We removed all phone numbers, inserted links to other
webpages, personal names, and content not specific to AST from the
policy documents that were retrieved from the websites of school boards,
municipalities, and transportation consortia.

In the final step, we removed all blank spaces, punctuation,
capitalization, and numbers. English stop words, which are common words
such as \emph{and} or \emph{the} as identified in a predetermined list
by Lewis et al. (Feinerer and Hornik, 2020) and other frequent terms in
the documents like ``school'' and specific location names, were removed
from the corpora.

@@

\hypertarget{framing-analysis}{%
\subsection{4.1. Framing analysis}\label{framing-analysis}}

Issues that pertain to public health or wellbeing are often presented to
the public through particular frames to influence perceptions or
behaviours. As previously mentioned, a frame is a ``central organizing
idea or story line that provides meaning'' to a public issue or
phenomenon (Gamson and Modigliani, 1987). Scholars in the field of
political communications have proposed that communicators, such as the
media or institutions, construct the narrative of a frame for policy
positions or public issues in order to activate or restrict a particular
response in the intended audience (Pan and Kosicki, 1993). Organized
groups of stakeholders can employ similar methods to attract attention
to particular issues. Framing can be used to position existing solutions
as suitable to address particular issues (Mah et al., 2014), which may
prevent the public from being aware of other policy approaches that
challenge the status quo. The way policy issues are framed is ultimately
important to understand because it plays a role in either altering or
preserving the existing social perceptions. Finally, the ideas that are
communicated by a particular frame can be either positive or negative
(\textbf{waygoodCO2ValenceFraming2018?}). There is evidence that
negative framing may be more effective at motivating individuals to
change transport modes to reduce CO2 emissions
(\textbf{waygoodCO2ValenceFraming2018?}).

\hypertarget{process}{%
\subsection{4.2. Process}\label{process}}

We use topic modelling in \texttt{R} to conduct the framing analysis.
Topic modelling is a machine learning technique used to analyze text to
identify the language and concepts being communicated. This method is
practical for researchers working with large amounts of text because it
replaces the manual coding of topics that would normally take place to
analyze or summarize textual data (Jacobi et al., 2016). In the data
pre-processing phase, we tokenize the text in the documents and create a
document-term matrix so that it is in the correct format for analysis.
We primarily use the following packages: \texttt{tidytext} (Robinson and
Silge, 2021), \texttt{topicmodels} (Grün and Hornik, 2021),
\texttt{word2vec} (Wijffels, 2021), and \texttt{wordcloud} (Fellows,
2018) to examine text in the documents that were sourced for this
project. These packages have functions for determining the frequency of
specific words in each document or relationships (e.g., pairs of
adjacent terms called bigrams) and correlations between words. Topic
modelling is a popular method for analyzing text from social media
platforms (Albalawi et al., 2020) and news articles (Jacobi et al.,
2016). We estimate latent Dirichlet allocation (LDA) models to classify
both the STP and academic documents according to the topics that are
contained within them. This method ``treats each document as a mixture
of topics, and each topic as a mixture of words'' (Silge and Robinson,
2021). The model's output is ``a set of topics consisting of clusters of
words that co-occur in these documents according to certain patterns''
(Jacobi et al., 2016). Researchers must then interpret the identified
topics, as done after other methods of manual coding. We also compare
the topics between the policy documents and the academic papers, and use
our interpretation to answer our research question. We describe in more
detail the functions and code in \texttt{R} that we used.

@@

This paper is an example of open and reproducible research that uses
only open software. All data are organized in the form of an open data
product (Arribas-Bel et al., 2021). Following best practices in spatial
data science (\textbf{brunsdon2020opening?}), the code and data needed
to reproduce our research or conduct a similar analysis for other
regions are available for download.

@@

We analyzed word and document frequency for each corpus of text. Table
\ref{tab:word-table} shows the most frequent terms found in the
municipal, transportation consortia, school board, and academic
documents. Policy documents and academic papers reference \emph{active},
\emph{travel}, \emph{walking}, \emph{biking} or \emph{cycling}, and
\emph{students} more than other terms. Each corpus also has
\emph{safety} and \emph{traffic} as common words which suggests that
such concerns are a common reason given for parents driving their
children to school. The word \emph{physical} is present in each corpus,
but it's not clear what this refers to (e.g, \emph{physical activity},
\emph{physical health}, or the \emph{physical environment}).
Furthermore, documents from STP stakeholder groups discuss
\emph{resources}, \emph{information}, and \emph{services} about school
travel. Unlike the academic papers, policy documents include the words
\emph{route} or \emph{routes} as frequent terms. This could indicate the
presence of ``safe routes to school'' in the policy corpus, as well as
the role of STP stakeholder groups in identifying safe routes to school
to share with parents or families. In the section below, the context in
which these terms are used is explored further.

@@

\caption{\label{tab:word-table}\label{tab:word-table}Top 25 terms identified in each corpora. Document frequencies are also indicated.}

@@

We then combined all municipality, school board, and transportation
consortia documents into one ``policy+practice'' corpus. This enabled us
to examine and visualize the most common bigrams found across all of the
material in Ontario that was collected for this study. Figure
\ref{fig:policy-visual} shows all of the bigrams that occur more than 10
times in the policy+practice corpus. In addition to the bigrams already
identified above, we also found \emph{mental health}, \emph{walk day},
and \emph{green communities} as common pairs of consecutive words.
\emph{Green Communities Canada} is a non-profit organization that has
significantly supported AST initiatives through the Ontario Active
School Travel program so the high frequency of this term in the
policy+practice corpus is not surprising. Overall, the policy documents
from STP stakeholder groups seem to focus on four key areas: i) benefits
or impacts of AST; ii) mechanisms of intervention; iii) concerns or
considerations; and iv) supports for AST. This interpretation indicates
that the general public accessing information about AST in Ontario is
informed about a wide range of content related to this issue.

Next, we analyzed bigrams in the academic corpus separately to make
comparisons with the policy+practice corpus. Figure
\ref{fig:academic-visual} indicates that academic papers include several
common bigrams that were also found in the policy documents including
\emph{physical activity} (n = 1566), which is the top bigram,
\emph{traffic safety} (n = 308), and \emph{safe routes} (n = 268).
However, many other factors are identified in the research literature
that are not presented to the general public through policy documents.
After \emph{physical activity}, \emph{built environment} (n = 1175),
\emph{independent mobility} (n = 774), and \emph{urban form} (n = 352)
are the most frequent pairs of consecutive words. Academic papers also
often discuss \emph{distance home} (n = 258), \emph{car ownership} (n =
254), \emph{household income} (n = 254), and \emph{population density}
(n = 205), which are factors that have been found to influence AST. Many
papers also investigate gender differences in AST given that \emph{boys
girls} (n = 211) is another common bigram. Finally, the presence of
\emph{statistically significant} among the top bigrams underscores that
researchers often aim to identify associations using statistical
measures. We found that the academic corpus focuses on a greater range
of topics than found in the policy documents.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-terms-1} \caption{\label{fig:policy-terms}Topics identified in the policy corpus according to clusters of words.}\label{fig:policy-terms}
\end{figure}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How is active school travel framed in Ontario, Canada?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{How is active school travel framed in Ontario, Canada?}
    \author[Some Department]{Author 1\corref{1}}
   \ead{author1@example.com} 
    \author[Some Department]{Author 2}
   \ead{author2@example.com} 
    \author[Another University]{Author 3\corref{2}}
   \ead{author3@example.com} 
    \author[Some Institute]{Author 4\corref{2}}
   \ead{author4@example.com} 
    \author[Some University]{Author 5}
   \ead{author5@example.com} 
    \author[Some Department]{Author 6}
   \ead{author6@example.com} 
      \address[Some Department]{Department, Street, City, Province,
Postal Code}
    \address[Another University]{Department, Street, City, Province,
Postal Code}
    \address[Some Institute]{Street, City, Province, Postal Code}
    \address[Some University]{Department, Street, City, Province, Postal
Code}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

  \begin{abstract}
  Active school travel (AST) has been increasingly encouraged by various
  stakeholders in Ontario, Canada through efforts such as school travel
  planning. Education strategies like workshops or resources that
  promote AST are commonly implemented. The framing of AST through such
  strategies may influence how walking and bicycling to school are
  perceived by parents. It may also draw attention to AST as an issue
  affecting children's health which could motivate behaviour change. We
  used natural language processing, including topic modelling, to
  examine how AST is framed in publicly available documents from Ontario
  stakeholders involved in school travel planning. We then compared the
  findings from these documents to a selection of studies on AST and
  explored similarities between the two. We found that AST is framed in
  two ways: i) as a health and environmental issue; and ii) as an
  accessible and feasible transport option for children and parents. The
  frames encourage children and parents to adopt AST given its health
  and environmental benefits by providing resources to support behaviour
  change. The benefits of AST and strategies to support AST that are
  communicated by stakeholders are consistent with the evidence from
  academic research. While these frames present AST in a positive light,
  they may not encourage parents to view current household travel
  behaviours as unhealthy for their children or their community.
  Stakeholders promoting AST in Ontario should further problematize the
  decline of AST and challenge the norm of driving children to school.

  Keywords: active school travel, school travel planning; natural
  language processing; framing analysis; education strategies
  \end{abstract}

@@

@@

Rates of walking and bicycling to school, commonly known as active
school travel (AST), have been declining in Canada and the United States
for decades (Rothman et al., 2018). However, the appetite for AST may be
high in many Canadian communities. For instance, in a study conducted in
Toronto, Ontario, 40\% of children who were driven to school stated they
would like to travel by bicycle instead (Larouche et al., 2016). The
study also reported that less than 3\% of respondents actually cycled,
despite the vast majority having access to a bicycle and living within a
short and bikeable distance to school. Another study based in London,
Ontario, reported similar findings with respect to children's preference
for active travel (Larsen et al., 2012). From a public health
perspective, increasing the use of active modes to school represents a
major opportunity to improve children's health and wellbeing.

The Government of Ontario, in Canada, has striven to promote this trend,
and created a fund in 2017 to support communities across the province to
develop AST initiatives. Green Communities Canada runs the program,
called \emph{Ontario Active School Travel} (G. C. Canada, 2020). As of
December 2021, OAST has awarded over CAD 2 million and provided
resources to over 25 projects across Ontario. Many communities
implemented school travel planning (STP), along with encouraging
activities like walking school buses and developed resources for schools
and parents, among other actions (see Canada, 2021). In this context,
STP is a popular ``school-specific'' intervention led by a facilitator
who brings together a committee of stakeholders from diverse sectors
including education, planning, transportation, and public health to
develop action plans (Buliung et al., 2011; Mammen et al., 2014a). The
five-step process involves identifying barriers to AST based on the
local context and implementing approaches or activities that make AST
safer and more convenient: 1) setup of the program; 2) data collection
and problem identification; 3) action planning; 4) implementation; 5)
monitoring and evaluation (Buliung et al., 2011; Lang et al., 2011).

@@

More recently, the literature has explored the link between transport
and children's wellbeing (Waygood et al., 2020), with relevant
applications to the study of travel satisfaction (van den Berg et al.,
2020; Westman et al., 2017b). Being driven to school reduces community
interactions for children, which may negatively impact their social
wellbeing (Waygood and Friman, 2015). In contrast, walking and bicycling
give children opportunities to socialize with friends or siblings
(Michail et al., 2021) and increase positive emotions that contribute to
wellbeing (Ramanathan et al., 2014). This is something that children
seem to value (Zwerts et al., 2010) and that tracks with findings among
university students (Páez and Whalen, 2010). More generally, social
connections through travel appear to be important for wellbeing.
Furthermore, AST can provide opportunities for children to engage with
natural environments (Fusco et al., 2012; Romero, 2015).

@@

Factors that influence AST have been presented and organized using a
socio-ecological model (SEM) (Mitra, 2013) or systems model (Badland et
al., 2016) whereby children's travel behaviour is understood within the
context of household, social, neighbourhood, and policy environments.
The SEM comes from the field of public health and is a useful framework
for understanding complex health behaviours, such as walking and
bicycling habits, This model helps to identify multiple determinants
that need to be addressed by interventions to facilitate behaviour
change. The consensus in the literature is that interventions should
target multiple levels in order to increase levels of healthy and
physically active modes of travel to school (Mitra, 2013). Rather than
describing an extensive list of factors that influence AST and mode
choice in Canada (e.g., Mammen et al., 2012; Mitra, 2013; Rothman et
al., 2018; Wilson et al., 2018), we discuss a few potentially modifiable
determinants that may be targeted for change through STP.

At the individual level, age is often positively associated with AST
(Mammen et al., 2012; Stark et al., 2018; Wilson et al., 2018). There is
evidence that gender is a determinant of AST, and that boys are more
likely to travel using active modes than girls, although this is not a
strong or consistent finding (Rothman et al., 2018; Schoeppe et al.,
2015). Children's mode choice to school is strongly influenced by their
parents' travel behaviours and the complexity of their household's
travel needs (Buliung et al., 2021), as well as daily parental support
(Mah et al., 2017). This indicates that shifting parental perceptions
and habits is important. Convenience and inclement weather have been
cited by parents as barriers to AST (Buliung et al., 2011). Parental
perceptions of the built or school environment (De Meester et al., 2014;
Panter et al., 2010) and their children's skills (Faulkner et al., 2010;
Mammen et al., 2012) also influence mode choice to school.

Distance between home and school is most negatively associated with AST
(Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009; Rothman et
al., 2018) with less AST reported among children who have to travel
farther to school - low density suburban development tends to increase
the need for movement, and the reliance on motorized modes (Farber and
Páez, 2011). Many studies have also found that the quality of the built
environment along the route to school and around the school site (Ikeda
et al., 2018; Rothman et al., 2021) and provision of active travel
infrastructure (Chen et al., 2018; Pont et al., 2009) facilitate AST.
Canadian youth report that they feel most safe bicycling on streets in
their neighbourhood or that have low volumes of traffic (T. A. of
Canada, 2020). Finally, concerns about traffic and strangers have been
reported by parents who drive their children to school (Mammen et al.,
2012), which highlights that the volume and speed of cars can be a
concern or deterrent for AST.

@@

School travel planning (STP) has been implemented in Canada since at
least the late 2000s. Within the STP process, facilitators generally
establish multi-sector committees which intervene at the participating
school through a range of activities related to the 4E's consisting of
\emph{education} strategies, \emph{encouragement} through in-person
events or programs, \emph{engineering} improvements to or around the
school site, and \emph{enforcement} of traffic speeds around schools
(Lang et al., 2011; Mammen et al., 2014b). The first large-scale
evaluation of STP as an intervention in Canada took place at twelve
schools across the country, including four in Ontario, using parental
surveys to measure changes in travel behaviour and perceptions (Buliung
et al., 2011). Following the intervention, active travel rates increased
across all schools and 14\% of parents reported a perceived reduction in
traffic outside the school (Buliung et al., 2011). Assessments of the
efficacy of STP (Buttazzoni et al., 2019; Mammen et al., 2014b) indicate
that it has the potential to encourage behaviour change and adoption of
AST. STP facilitators have recommended that additional time and
resources are needed to improve the efficacy of STP (Mammen et al.,
2015), which highlights that long-term and sustained efforts driven at
the policy level are required to address declining rates of AST.

How AST is framed seems particularly important to shift parental
attitudes and perceptions, given their reported influence on children's
travel mode to school. STP activities heavily focus on education or
encouragement (Buliung et al., 2011; Buttazzoni et al., 2018; Mammen et
al., 2014b), but parents may not always be receptive to the goals of STP
and may be resistant to behaviour change (Buttazzoni et al., 2018).
Parents have been found to express different understandings, language,
and perceptions than planners of how the built environment can influence
school travel (Buliung et al., 2021). This is also true when it comes to
other factors like convenience of different modes to school (Lang et
al., 2011). STP stakeholders must pay special attention to parents'
understanding of the decline of AST as a problem, which may affect their
receptivity to proposed solutions.

The ``central organizing idea or story line'' of AST, to apply the
definition of framing from Gamson and Modigliani (1987), could also
affect broader support in the community. Municipal representatives are
perceived to be instrumental but the involvement of other stakeholder
groups (e.g., busing consortia representatives and local residents) can
be lacking (Buttazzoni et al., 2018). In Ontario, it is reasonable to
say that AST has become a policy issue on the education and public
health agendas, supported, albeit in a modest way, by financial
contributions from the provincial government\footnote{To put the CAD 2
  million invested by the province in the Ontario Active School Travel
  program in perspective, a city such as Hamilton budgeted in excess of
  CAD 91 million on road maintenance and construction in 2016 alone;
  see:
  https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets}.
Still, the support from a range of municipal representatives (see
Buttazzoni et al., 2018; Mammen et al., 2015) demonstrates that the AST
issue is on the political agenda. However, it is unknown to what degree
the general public (i.e., local residents) has been exposed to messaging
about AST.

@@

\hypertarget{framing-analysis}{%
\subsection{2.4. Framing Analysis}\label{framing-analysis}}

Issues that pertain to public health or wellbeing are often presented to
the public through particular frames to influence perceptions or
behaviours. As previously mentioned, a frame is a ``central organizing
idea or story line that provides meaning'' to a public issue or
phenomenon (Gamson and Modigliani, 1987). Scholars in the field of
political communications have proposed that communicators, such as the
media or institutions, construct the narrative of a frame for policy
positions or public issues in order to activate or restrict a particular
response in the intended audience (Pan and Kosicki, 1993). Organized
groups of stakeholders can employ similar methods to attract attention
to particular issues. Framing can be used to position existing solutions
as suitable to address particular issues (Mah et al., 2014), which may
prevent the public from being aware of other policy approaches that
challenge the status quo. The way policy issues are framed is ultimately
important to understand because it plays a role in either altering or
preserving the existing social perceptions. Finally, the ideas that are
communicated by a particular frame can be either positive or negative
(Waygood and Avineri, 2018). There is evidence that negative framing may
be more effective at motivating individuals to change transport modes to
reduce CO2 emissions (Waygood and Avineri, 2018).

@@

We also manually removed any extraneous material that did not pertain to
AST specifically. For the academic papers, this included footnotes,
references, acknowledgments, and conflict of interest statements. For
the policy+practice documents, it included phone numbers, inserted links
to other webpages, personal names, and content not specific to AST. In
the final step, we removed all blank spaces, punctuation,
capitalization, and numbers. English stop words, which are common words
such as \emph{and} or \emph{the} as identified in a predetermined list
by Feinerer and Hornik (2020) and other frequent terms in the documents
like ``school'' and specific location names, were removed from the
corpora.

@@

\hypertarget{process-of-framing-analysis}{%
\subsection{4.1. Process of Framing
Analysis}\label{process-of-framing-analysis}}

We use topic modelling in \texttt{R} to conduct the framing analysis.
Topic modelling is a machine learning technique used to analyze text to
identify the language and concepts being communicated. This method is
practical for researchers working with large amounts of text because it
replaces the manual coding of topics that would normally take place to
analyze or summarize textual data (Jacobi et al., 2016). In the data
pre-processing phase, we tokenize the text in the documents and create a
document-term matrix so that it is in the correct format for analysis.
We primarily use the following packages: \texttt{tidytext} (Robinson and
Silge, 2021), \texttt{topicmodels} (Grün and Hornik, 2021),
\texttt{word2vec} (Wijffels, 2021), and \texttt{wordcloud} (Fellows,
2018) to examine text in the documents that were sourced for this
project. These packages have functions for determining the frequency of
specific words in each document or relationships (e.g., pairs of
adjacent terms called bigrams) and correlations between words. Topic
modelling is a popular method for analyzing text from social media
platforms (Albalawi et al., 2020) and news articles (Jacobi et al.,
2016). We estimate latent Dirichlet allocation (LDA) models to classify
both the STP and academic documents according to the topics that are
contained within them. This method ``treats each document as a mixture
of topics, and each topic as a mixture of words'' (Silge and Robinson,
2022). The model's output is ``a set of topics consisting of clusters of
words that co-occur in these documents according to certain patterns''
(Jacobi et al., 2016). Researchers must then interpret the identified
topics, as done after other methods of manual coding. We also compare
the topics between the policy documents and the academic papers to
interpret what is being communicated by STP stakeholders. We describe in
more detail the functions and code in \texttt{R} that we used.

@@

This paper is an example of open and reproducible research that uses
only open software. Following best practices in spatial data science
(Brunsdon and Comber, 2020), the code and data needed to reproduce our
research or conduct a similar analysis for other regions are available
for download upon request.

@@

We analyzed word and document frequency for each corpus of text. Table
\ref{tab:word-table} shows the most frequent terms found in the
municipal, transportation consortia, school board, and academic
documents. Policy documents and academic papers reference \emph{active},
\emph{travel}, \emph{walking}, \emph{biking} or \emph{cycling}, and
\emph{students} more than other terms. Each corpus also has
\emph{safety} and \emph{traffic} as common words which suggests that
these are common concerns for parents. The word \emph{physical} is
present in each corpus, but it's not clear what this refers to (e.g,
\emph{physical activity}, \emph{physical health}, or the \emph{physical
environment}). Furthermore, documents from STP stakeholder groups
discuss \emph{resources}, \emph{information}, and \emph{services} about
school travel. Unlike the academic papers, policy documents include the
words \emph{route} or \emph{routes} as frequent terms. This could
indicate the presence of ``safe routes to school'' in the policy corpus,
as well as the role of STP stakeholder groups in identifying safe routes
to school to share with parents or families. In the section below, the
context in which these terms are used is explored further.

@@

\caption{\label{tab:word-table}\label{tab:word-table}Top 25 terms identified in each corpus. Document frequencies are also indicated.}

@@

We then combined all municipality, school board, and transportation
consortia documents into one ``policy+practice'' corpus. This enabled us
to examine and visualize the most common bigrams found across all of the
material in Ontario that was collected for this study. Figure
\ref{fig:policy-visual} shows all of the bigrams that occur more than 10
times in the policy+practice corpus. In addition to the bigrams already
identified above, we also found \emph{mental health}, \emph{walk day},
and \emph{green communities} as common pairs of consecutive words.
\emph{Green Communities Canada} is a non-profit organization that has
significantly supported AST initiatives through the Ontario Active
School Travel program so the high frequency of this term in the
policy+practice corpus is not surprising. Overall, the policy documents
from STP stakeholder groups seem to focus on four key areas: i) benefits
or impacts of AST; ii) mechanisms of intervention; iii) concerns or
barriers; and iv) supports for AST. This interpretation indicates that
the general public accessing information about AST in Ontario is
informed about a wide range of content related to this issue.

Next, we analyzed bigrams in the academic corpus separately to make
comparisons with the policy+practice corpus. Figure
\ref{fig:academic-visual} indicates that academic papers include several
common bigrams that were also found in the policy documents including
\emph{physical activity} (n = 1566), which is the top bigram,
\emph{traffic safety} (n = 308), and \emph{safe routes} (n = 268).
However, many other factors are identified in the research literature
that are not presented to the general public through policy documents.
After \emph{physical activity}, \emph{built environment} (n = 1175),
\emph{independent mobility} (n = 774), and \emph{urban form} (n = 352)
are the most frequent pairs of consecutive words. Academic papers also
often discuss \emph{distance home} (n = 258), \emph{car ownership} (n =
254), \emph{household income} (n = 254), and \emph{population density}
(n = 205), which are factors that have been found to influence AST. Many
papers also investigate gender differences in AST given that \emph{boys
girls} (n = 211) is another common bigram. Finally, the presence of
\emph{statistically significant} among the top bigrams indicates that
researchers often aim to identify associations using statistical
measures. We found that the academic corpus focuses on a greater range
of topics than found in the policy+practice documents.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-terms-1} \caption{\label{fig:policy-terms}Topics identified in the policy+practice corpus according to clusters of words. The per-word-per-topic probabilities are shown by beta.}\label{fig:policy-terms}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-terms-1} \caption{\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words. The per-word-per-topic probabilities are shown by beta.}\label{fig:academic-terms}
\end{figure}
